Tsbrowse: an interactive browser for Ancestral Recombination Graphs

### 2025-06-19 manuscript/revision/response_to_editor.tex

\begin{document}

\begin{letter}{}

\opening{Dear Alison,}

We are delighted to receive such positive feedback, and thank the reviewers for their 
careful consideration of the manuscript and software, and the constructive and helpful 
input provided. Attached are the revised manuscript (\textit{paper.pdf}), 
a version of the manuscript showing the differences to the submitted version 
(\textit{main\_diff.pdf, supplement\_diff.pdf}), and a response to the reviewers' comments 
(\textit{response\_to\_reviwers.pdf})

### 2025-06-20 manuscript/revision/response_to_reviewers.tex

Summary: In this manuscript, the authors present tsbrowse, an open-source Python-based 
application for the interactive visualization of the components of Ancestral Recombination 
Graphs (ARGs). Because ARGs (in principle) contain all knowable information concerning 
coalescence and recombination in the history of a set of samples, there is great excitement 
in developing methods for inferring ARGs from empirical genomic sequence data, as well as 
for learning about evolutionary processes from patterns in inferred ARGs. A crucial component 
of both these endeavors is visualizing ARGs, which is difficult or unwieldy. Tsbrowse therefore 
represents an exciting contribution to the field which is likely to be of high utility and 
to be highly cited.

Opinion: This paper was straightforward, clear, and well written. I think it does a good job 
setting up the intellectual context for ARG-based research and advocating for the utility of 
tsbrowse. I had two minor, nitpicky comments, but overall, it was great. Thanks for a fun and 
easy review!\\
\textcolor{blue}{Thank you for your kind words!}

1. I think the order in which the supplemental figures are cited doesn’t match their numbering 
(i.e., S4 is cited before S1)\\
\textcolor{blue}{We have now rearranged the supplementary figures so that figure references 
appear in ascending order.}

2. In the discussion, the authors mention that methods for visualization of tree topology can 
typically only handle a few hundred nodes, but it might be worth doing a ``(but see…)'' for some 
of the approaches folks have taken for visualizing much larger trees (e.g., nextstrain, onezoom).\\
\textcolor{blue}{We had already included a citation to the OneZoom project (and the Treenome browser) in the 
sentence that followed the one in question "… Visualisation of large-scale tree topologies with millions of nodes 
requires much more sophisticated approaches to capture topological features at different scales, 
and is an active research area". Thanks for bringing Nextstrain to our 
attention, and we have now included \href{{https://academic.oup.com/bioinformatics/article/34/23/4121/5001388}}{Hadfield et al.} 
as a citation for visualisation of medium-sized toplogies.}\\

### 2025-06-20 manuscript/supplement.tex
jk review response

\subsection{Inference of selective sweep dataset (Fig.~S\ref{fig:Supplementary_Figure_3})} 
The following software was used to infer ARGs from the truth dataset described in the
section 'Simulation of truth dataset' above: 
\texttt{tsinfer version 0.3.3}
\citep{kelleher2019inferring}, \texttt{tsdate version 0.2.1}, 
\texttt{Relate version 1.2.2} \citep{speidel2019method}, 
\texttt{ARG-needle version 1.0.3} \citep{zhang2023biobank},
\texttt{SINGER version 0.1.8-beta} \citep{deng2024robust}.
For all inferences, the following parameters were used: \textit{recombination
    rate = 1e-8}, \textit{mutation rate = 1e-8}, \textit{effective population size
    = 10,000}. Default values were used for other parameters.

>>>>

\subsection{Inference of selective sweep dataset (Fig.~S\ref{fig:Supplementary_Figure_3})} 
The following software was used to infer ARGs from the truth dataset described in the
section ``Simulation of truth dataset'' above: 
\texttt{tsinfer version 0.3.3}
\citep{kelleher2019inferring}, \texttt{tsdate version 0.2.1}, 
\texttt{Relate version 1.2.2} \citep{speidel2019method}, 
\texttt{ARG-needle version 1.0.3} \citep{zhang2023biobank},
\texttt{SINGER version 0.1.8-beta} \citep{deng2024robust}.
For all inferences, the following parameters were used: \textit{recombination
    rate = 1e-8}, \textit{mutation rate = 1e-8}, \textit{effective population size
    = 10,000}. Default values were used for other parameters.
